---
title: "represtools"
author: "Brian A. Fannin"
date: "`r Sys.Date()`"
output: 
  slidy_presentation:
    css: My.css
---

# Overview

> The focus is less on the equations and more on the equator.

# Inspiration

* Reproducible Research by Christropher Gandrud
* `devtools` by Hadley Wickham.

# Guiding principals

- Units of work should be modular. Build analytic steps like building functions.
- All work takes place in .Rmd files.
- The only form of data exchange between steps is .rda.
- Recreate when necessary and only when necessary

# Other stuff

* Common external data sources like SQL and URL should be easy to deal with.
* Version control easily built in

# 4 principal stages: 

The four steps are verbs. Their outputs are adjectives which describe the data contained. Each step may work in isolation, so long as precedent data exists.

> - gather
> * cook
> * analyze 
> * present

# A sample workflow

```{r eval=FALSE}
represtools::NewResearch("Baseball")
represtools::Gather("Hitters")
# write some code
represtools::Cook("Hitters")
# write some code
represtools::Analyze("Handedness")
# write some code
represtools::Present("Handedness", title = "On the quality of right-handed batters")
# write some code
represtools::Make()
represtools::AddGitRemote(Name = "origin", URL = "https://github.com/PirateGrunt/raw.git")
```

And that would do it.

# NewResearch

* Create a new set of directories
* Copy the Makefile
* git init

# Verbs

* Copy the markdown skeleton to the appropriate directory.
* Control what files are used for input. Only one output file.
* Default behavior is to 

```{r eval = FALSE}
represtools::Gather("Pitchers")
represtools::Cook("Players", inputFiles = c("Hitters", "Pitchers"))
```

# Make

Simply put, Make does the following:

* Make only runs those elements of your project which are needed. 
* It's possible to construct various "recipes" which different
* `Make` comes with RStudio

```{r eval=FALSE}
represtools::Make()
represtools::Make("clean")
```

# Questions

* Why not .rds? Short answer: only saves a single object
* What's wrong with ProjectTemplate? Short answer: nothing
* Why not rake or waf? Short answer: I'm not familiar with these tools.
